\documentclass[a4paper]{article}
\usepackage{tabularx}
\usepackage{ae}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{CV}
\usepackage[left=1.5cm,top=1cm,right=1.5cm,nohead,nofoot]{geometry}
\begin{document}
\pagestyle{empty}
\begin{center}

\Large
\textsc{Johny James}% right
\end{center}
\vspace{1.2\baselineskip}
\begin{flushleft}
    Senior Software Engineer \\
    CouponDunia \\
    Phone : +918086586959 \\
    Email : kjjohny1991@gmail.com \\
    Github : \url{https://github.com/nu11p01n73R} \\ 
    StackOverflow : \url{http://stackoverflow.com/users/3150943/nu11p01n73r}
\end{flushleft}

\section{Objective}
\begin{flushleft}
    To pursue a challenging career in an organization where my knowledge and skills will be
    utilized to the fullest extent and will provide a platform for career growth and learning.
\end{flushleft}

\section{Technical Skills}
\begin{flushleft}
    Python, PHP, Javascript, C/C++, MySQL, Algorithms, Regular Expressions, Nginx, AWS, Git, Shell Scripting, Awk, Go, Angular2, ElasticSearch, NodeJs, \LaTeX
\end{flushleft}

\section{Experience}
\begin{CV}
\item[June 2015 -- Present]
    ~\\
    CouponDunia\\
    Senior Software Engineer\\
    \emph{Technologies} - PHP, Javascript, Git, MySQL, Redis, AWS, Angular2, Yii2, NodeJS, Socket.io, ElasticSearch, Docker \\\\
    \emph{coupondunia.in} Working as a full stack developer. Architectured a micro-service system, which web facing API layer
    written in PHP using a custom framework, build on top of Slim3. Developed a search service using ElasticSearch which serves 
    the search requests on the site. Worked on frontend web app written in Angular2. Worked also as a Dev-Ops, mainly responsible for
    service uptime and release management. Have experience working with AWS resources, nginx web servers, linux systems etc. Build a
    development environment using Docker for the different services.\\\\
    \emph{goswag.com} Involved in designing and building the system. Mostly wrote backend on PHP on Yii2. Later involved in refactoring 
    the code to a client side app on AngularJS.\\
\end{CV}

\begin{CV}
\item[August 2014 -- May 2015]
    ~\\
    Cognizant Technology Solutions\\
    Programmer Analyst Trainee\\
    \emph{Technologies} C, MySQL, Java.
\end{CV}

\section{Personal Details}
\begin{flushleft}
    \begin{tabular}{ll}
        Nationality : & Indian\\
        Date of birth : & 20-09-1991 \\
        Languages known : & English, Malayalam
    \end{tabular}
\end{flushleft}


\section{Project Summary}
\begin{tabular}{r|p{15cm}}
    \emph{GitHub}  & More open source projects on github, \normalsize{\url{https://github.com/nu11p01n73R}} \\
    \multicolumn{2}{c}{}\ %this clears the space between two jobs
\end{tabular}

\begin{tabular}{r|p{15cm}}
    \emph{B.Tech} & Mini Project \\
    \textsc{2013} & \emph{Modelling GPU} \\
    & \normalsize{The project was to model a graphical processing unit on a Field programmable gate array(FPGA) board using verilog. Instructions are then send over to the modelled processor from a system through serial port which is stored on a modelled RAM. These instructions are then fetched decoded and executed on the ALU unit modelled on the board.}\\
    \multicolumn{2}{c}{}\ %this clears the space between two jobs
\end{tabular}

\begin{tabular}{r|p{15cm}}
    \emph{B.Tech} & Main Project \\
    \textsc{2013} & \emph{Task Scheduler For Embedded System(In Progress)} \\
    & \normalsize{Static task scheduler for embedded systems for use on automobile}\\
    \multicolumn{2}{c}{} %this clears the space between two jobs %some other job here \end{tabular} \begin{tabular}{r|p{15cm}}
\end{tabular}

\begin{tabular}{r|p{15cm}}
    \emph{B.Tech} & Human Machine Interaction \\
    \textsc{2013} & \emph{Fluid Interface} \\
    & \normalsize{This is an application which makes use of kinect gaming console to detect the motion of person within an area and plot the path through which the person moves.}\\

    \textsc{2013} & \emph{Virtual Notepad} \\
    & \normalsize{The virtual notepad is an application which lets the user take advantage of an infrared pen to write or draw on a virtual}\\
    \multicolumn{2}{c}{}\ %this clears the space between two jobs
\end{tabular}

\section{Achievements}
\begin{itemize}
    \item 19.6K Reputation on StackOverflow.
    \item Received two STAR awards at CouponDunia for performance.
\end{itemize}

\section{Talks}
\begin{itemize}
    \item Workshop on Golang at ICEFOSS 2016, FISAT
\end{itemize}

\section{Education}
\begin{CV}
\item[2010 -- 2014] B.Tech Computer Science \& Engineering (seventh semester) \\
    Institution : Federal Institute Of Science And Technology Angamaly \\
    University : MG University \\
    Status : 7.8 CGPA 
\end{CV}

\section{Declaration}
I hereby declare that the above furnished information is true to best of my knowledge and belief \\ \\ \\
\vspace{5\baselineskip}
\textbf {Date :} \hfill \textbf{Johny James}

\end{document}






